---
title: "Block Processing Report"
date: "`r Sys.Date()`"
params:
  HwInfo: (Hardware Info)
  OsInfo: (OS Info)
  Machine: (Machine Info)
  GoInfo: (GO Info)
  GitHash: (GithubKey)
  StateDB: (StateDB)
  VM: (VM)
  db: ./test.db
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
con <- dbConnect(SQLite(), params$db)
blockData <- dbReadTable(con, 'blockProfile')
reducedBlockData <- dbReadTable(con, 'aggregatedBlockProfile')
txData <- dbReadTable(con, 'TxProfile')
reducedTxData <- dbReadTable(con, 'aggregatedTxProfile')
dbDisconnect(con)
```

## 1. Experimental Setup
The experiment is run on the machine `r params$Machine`, which is a `r params$HwInfo` computer.
The operating system is `r params$OsInfo`.
The system has installed `r params$GoInfo`.
The github hash of the Aida repository is `r params$GitHash`.
For this experiment, we use **`r params$StateDB`** as a StateDB and **`r params$VM`** as a virtual machine.
The data set for this experiment is stored in the database `r params$db`.

## 2. Block Processing Time

The experiment was conducted for the block range from **`r format(min(blockData$block),big.mark=",")`**  to **`r format(max(blockData$block),big.mark=",")`**. 
The block range contains **`r format(sum(blockData$numTx), big.mark=",")`** transactions.
The accumulated block processing time is **`r format(sum(blockData$tBlock)/(1e9*3600), digits=3, nsmall=2)`** hours. The block rate is `r format(1e9*(max(blockData$block)-min(blockData$block)+1)/sum(blockData$tBlock), digits=3, nsmall=2)` blocks per second.
The average block execution time is `r format(mean(blockData$tBlock)/1e6, digits=3, nsmall=3)` milliseconds, with a minimum of `r format(min(blockData$tBlock)/1e3, digits=3, nsmall=3)` microseconds and a maximum of `r format(max(blockData$tBlock)/1e9, digits=3, nsmall=3)` seconds.
The smoothened trend line for the block time (in milliseconds) is shown below. In the figure, we aggregated the block time for all 100K blocks shown as points.

```{r, echo=FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = tBlock)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="Block Time (ms)", title="Block Processing Time")
```

## 3. Commit Time

The average commit time of a block is `r format(mean(blockData$tCommit)/1e3, digits=3, nsmall=3)` microseconds, with a minimum of `r format(min(blockData$tCommit), digits=3, nsmall=3)` nanoseconds and a maximum of `r format(max(blockData$tCommit)/1e9, digits=3, nsmall=3)` seconds.
The smoothened trend line of the commit time of a block is shown below. In the figure, we aggregated the commit time in microseconds for all 100K blocks shown as points.

```{r, echo = FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = tCommit)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="Commit Time (us)", title="Commit Time")
```


## 4. Gas Consumption of Blocks

The average gas consumption of a block is `r format(mean(blockData$gasBlock)/1e6, digits=3, nsmall=3)` MGas, with a minimum of `r format(min(blockData$gasBlock)/1e3, digits=3, nsmall=3)` KGas and a maximum of `r format(max(blockData$gasBlock)/1e6, digits=3, nsmall=3)` MGas.
The smoothened trend line of gas consumption is shown in the figure below. In the figure, we aggregate the gas consumption for all 100K blocks as points.

```{r, echo = FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = gasBlock)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="MGas", title="Gas Consumption of Blocks")
```

## 5. Number of Transactions per Block

We have an average  of `r format(mean(blockData$numTx), digits=3, nsmall=3)` transactions per block.
The smallest number of transactions in a block is `r min(blockData$numTx)`, and the largest number of transactions in a block is `r max(blockData$numTx)`.
The histogram of the number of transactions in a block is shown below:

```{r, echo = FALSE, message=FALSE}
hist(blockData$numTx, freq=FALSE, main="Number of Transaction Distribution", xlab="Number of Transactions", col="lightblue1"); rug(blockData$numTx)
abline(v=mean(blockData$numTx), col="dodgerblue3", lty=2, lwd=2)
```

The smoothened trend line for the number of transactions in a block is shown below. In this figure, we aggregated the number of transactions in a block for 100K blocks shown as points.

```{r, echo=FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = numTx)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="Number of Transactions", title="Number of Transactions per Block")
```

## 5. Transaction Processing Time

The average transaction processing time is `r format(mean(txData$duration)/1e3, digits=3, nsmall=3)` microseconds, with a minimum of `r format(min(txData$duration)/1e3, digits=3, nsmall=3)` microseconds and a maximum of `r format(max(txData$duration)/1e9, digits=3, nsmall=3)` seconds.
The smoothened trend line of the transaction processing time is shown in the figure below. In the figure, we aggregated the transaction processing time for one million transactions shown as points.

```{r, echo=FALSE, message=FALSE}
reducedTxData %>%
  ggplot(aes(x = tx, y = duration)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Transactions", y="Processing Time (us)", title="Transaction Processing Time")
```

## 6. Gas Consumption of Transactions

The average gas consumption of a transaction is `r format(mean(blockData$gas)/1e6, digits=3, nsmall=3)` MGas, with a minimum gas consumption of `r format(min(blockData$gas)/1e3, digits=3, nsmall=3)` KGas and a maximum gas consumption of `r format(max(blockData$gas)/1e6, digits=3, nsmall=3)` MGas.
The smoothened trend line of gas consumption is shown below. In the figure, we aggregated the gas consumption for one million transactions shown as points.

```{r, echo=FALSE, message=FALSE}
reducedTxData %>%
  ggplot(aes(x = tx, y = gas)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Transactions", y="KGas", title="Gas Consumption of Transactions")
```

## 7. Transaction Throughput

For all blocks, we achieve a throughput of `r format(1e9*sum(blockData$numTx)/sum(blockData$tBlock), digits=3, nsmall=3)` transactions per second.
The smoothened trend line of the throughput is shown in the figure below. The throughput is aggregated for each 100K blocks shown as points.

```{r, echo=FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = tps)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="Transactions Per Second", title="Throughput in Transactions per Second")
```

## 8. Gas Rate

We achieve a gas rate of `r format(1e3*sum(blockData$gas)/sum(blockData$tBlock), digits=3, nsmall=3)` MGas per second.
The smoothened trend line of the gas rate for each 100K blocks is shown in the figure below as points.

```{r, echo=FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = gps)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="MGas Per Second", title="Throughput in MGas per Second")
```
