---
title: "Mainnet Report"
date: "`r Sys.Date()`"
params:
  HwInfo: (Hardware Info)
  OsInfo: (OS Info)
  Machine: (Machine Info)
  GoInfo: (GO Info)
  GitHash: (GithubKey)
  StateDB: (StateDB)
  VM: (VM)
  db: ./test.db
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
library(gt)

# open database
con <- dbConnect(SQLite(), params$db)

# load block and transaction tables into data frames
blockData <- dbReadTable(con, 'blockProfile')
txData <- dbReadTable(con, 'TxProfile')

# compress block dataframe for each 100K blocks
block_group_size <- 100000
blockData$block_group <- blockData$block %/% block_group_size
reducedBlockData <- blockData %>% group_by(block_group) %>% summarise(numTx=mean(numTx),           # average number of transactions
                                                                      gasBlock=mean(gasBlock)/1e6) # average gas (in MGas)
reducedBlockData$block <- reducedBlockData$block_group * block_group_size
blockData$block_group <- NULL

# compress transactional data for each 1M transactions
tx_group_size <- 1000000
txData$tx_group <- 1:nrow(txData) %/% tx_group_size
reducedTxData <- txData %>% group_by(tx_group) %>% summarise(duration=mean(duration)/1e3,  # average duration (in us)
                                                             gas=mean(gas)/1e3)            # average gas (in KGas)
reducedTxData$tx <- reducedTxData$tx_group * tx_group_size
txData$tx_group <- NULL

# close database connection
dbDisconnect(con)
```

The following report characterises the mainnet including charts related to block and transaction complexity.
The report covers the block range from **`r format(min(blockData$block),big.mark=",")`**  to **`r format(max(blockData$block),big.mark=",")`**.
The block range contains **`r format(sum(blockData$numTx), big.mark=",")`** transactions.
We have **`r format((max(blockData$block)-min(blockData$block)+1)-nrow(blockData), big.mark=",")`** empty blocks.

## 1. Number of Transactions per Block

We have an average  of `r format(mean(blockData$numTx), digits=3, nsmall=3)` transactions per block.
The smallest number of transactions in a block is `r min(blockData$numTx)`, and the largest number of transactions in a block is `r max(blockData$numTx)`.
The histogram of the number of transactions in a block is shown below:

```{r, echo = FALSE, message=FALSE}
hist(blockData$numTx, freq=FALSE, main="Number of Transaction Distribution", xlab="Number of Transactions", col="lightblue1"); rug(blockData$numTx)
abline(v=mean(blockData$numTx), col="dodgerblue3", lty=2, lwd=2)
```

The smoothened trend line for the number of transactions in a block is shown below. In this figure, we aggregated the number of transactions in a block for 100K blocks shown as points.

```{r, echo=FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = numTx)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="Number of Transactions", title="Number of Transactions per Block")
```

The numbers and the figure above include maintenance transactions as well (SFC, etc.).

Transactions are either wallet transfers, smart contract executions, smart contract creations, and maintenance contracts.
```{r, echo=FALSE, message=FALSE}
txTypeDf <- txData %>% count(txType)
txTypeDf$label <- c("Wallet Transfer", "Contract Creation", "Contract Execution", "Maintenance Contract")
txTypeDf$percent <- round(100 * txTypeDf$n / sum(txTypeDf$n), 1)
pie(txTypeDf$n, labels = paste0(txTypeDf$label, " (", txTypeDf$percent, "%)"), main ="Transaction Types")
```

## 2. Gas Consumption of Blocks

The average gas consumption of a block is `r format(mean(blockData$gasBlock)/1e6, digits=3, nsmall=3)` MGas, with a minimum of `r format(min(blockData$gasBlock)/1e3, digits=3, nsmall=3)` KGas and a maximum of `r format(max(blockData$gasBlock)/1e6, digits=3, nsmall=3)` MGas.
The top seven most gas-consuming blocks are the following:
```{r echo=FALSE, message=FALSE}
top7Blocks <- blockData %>% top_n(7, gasBlock) %>% select(block, gasBlock) %>% arrange(desc(gasBlock)) %>% rename(Block = block, Gas = gasBlock)
gt(top7Blocks)
```


The smoothened trend line of gas consumption is shown in the figure below. In the figure, we aggregate the gas consumption for all 100K blocks as points.

```{r, echo = FALSE, message=FALSE}
reducedBlockData %>%
  ggplot(aes(x = block, y = gasBlock)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Block Height", y="MGas", title="Gas Consumption of Blocks")
```

## 3. Gas Consumption of Transactions

The average gas consumption of a transaction is `r format(mean(txData$gas)/1e3, digits=3, nsmall=3)` KGas, with a minimum gas consumption of `r format(min(txData$gas)/1e3, digits=3, nsmall=3)` KGas and a maximum gas consumption of `r format(max(txData$gas)/1e6, digits=3, nsmall=3)` MGas.
The top seven most gas-consuming transactions are the following:
```{r echo=FALSE, message=FALSE}
top7Transactions <- txData %>% top_n(7, gas) %>% select(block, tx, gas) %>% arrange(desc(gas)) %>% rename(Gas = gas, Block = block, Transaction = tx)
gt(top7Transactions)
```

The gas consumption based on the transaction type is shown below:

```{r, echo=FALSE, message=FALSE}
txGasTypeDf <- txData %>% group_by(txType) %>% summarize(gas=sum(gas))
txGasTypeDf$label <- c("Wallet Transfer", "Contract Creation", "Contract Execution", "Maintenance Contract")
txGasTypeDf$percent <- round(100 * txGasTypeDf$gas / sum(txGasTypeDf$gas), 1)
pie(txGasTypeDf$gas, labels = paste0(txGasTypeDf$label, " (", txGasTypeDf$percent, "%)"), main ="Gas Consumption of Transaction Types")
```

The smoothened trend line of gas consumption over all transaction is shown below. In the figure, we aggregate the gas consumption for one million transactions shown as points. The numbers and the figure below include maintenance transactions as well (SFC, etc.).

```{r, echo=FALSE, message=FALSE}
reducedTxData %>%
  ggplot(aes(x = tx, y = gas)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Transactions", y="KGas", title="Gas Consumption of Transactions")
```

## 4. Gas Consumption for Transaction Types
### Wallet Transfers

```{r, echo=FALSE, message=FALSE}
WalletTransferDf <- txData %>% filter(txType == 0)
hist(WalletTransferDf$gas, main="Histogram for Wallet Transfers", freq=FALSE, xlab="Gas Consumption", col="lightblue1")
```

### Contract Creation

```{r, echo=FALSE, message=FALSE}
ContractCreationDf <- txData %>% filter(txType == 1)
hist(ContractCreationDf$gas, main="Histogram for Contract Creations", freq=FALSE, xlab="Gas Consumption", col="lightblue1")
```

### Contract Execution

```{r, echo=FALSE, message=FALSE}
ContractExecutionDf <- txData %>% filter(txType == 2)
hist(ContractExecutionDf$gas, main="Histogram for Contract Executions", freq=FALSE, xlab="Gas Consumption", col="lightblue1")
```

### Maintenance Contract

```{r, echo=FALSE, message=FALSE}
MaintenanceContractDf <- txData %>% filter(txType == 3)
hist(MaintenanceContractDf$gas, main="Histogram for Maintenance Contract (SFC, etc.)", freq=FALSE, xlab="Gas Consumption", col="lightblue1")
```
