---
title: "Parallelisation Experiment"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library(DBI)
library(RSQLite)
con <- dbConnect(SQLite(), "./profile.db")
experiment <- dbReadTable(con, 'parallelprofile')
parallelisable <- experiment %>%
  filter(speedup > 1.0)
dbDisconnect(con)
```

## 1. Block Range

The experiment was performed on the block range from `r format(min(experiment$block),big.mark=",")` 
to `r format(max(experiment$block),big.mark=",")`.

## 2. Degree of Parallelisation 

We have `r format(nrow(experiment), big.mark=",")` blocks of which 
`r format(nrow(parallelisable), big.mark=",")` are parallelisable.
`r format(100.0*(nrow(experiment)-nrow(parallelisable))/nrow(experiment), digits=4)`% of blocks are 
strictly sequential (not parallelisable) blocks. 
The maximal achievable parallelism of a block is `r format(max(experiment$speedup), digits=4)`.
The geometric mean of the speedup is `r format(exp(mean(log(experiment$speedup))), digits=4)`.

The distribution of the speedup is shown below:
```{r, echo = FALSE}
experiment %>% 
  ggplot(aes(speedup)) + 
  geom_freqpoly(binwidth = 0.01)
```

## 3. Number of Transactions per Block

We have on average `r mean(experiment$numTx)` transactions per block. The 
smallest number of transactions per block is `r min(experiment$numTx)` and the 
largest number is `r max(experiment$numTx)`. The distribution of number of 
transactions per block is shown below:

```{r, echo = FALSE}
experiment %>% 
  ggplot(aes(numTx)) + 
  geom_freqpoly(binwidth = 0.01)
```

## 4. Processor Utilisation / Efficiency

The lower bound of the processor utilisation is `r format(100.0*exp(mean(log(experiment$speedup/experiment$ubNumProc))), digits=4)`% on average and with a maximum of `r max(experiment$ubNumProc)` processors (upper bound).

## 5. Sequential Block Runtime and Commit Time

The average block execution time is `r mean(experiment$tBlock)/1e6` milliseconds with 
a minimum of `r min(experiment$tBlock)/1e6` milliseconds and a maximum of `r max(experiment$tBlock)/1e6` milliseconds. 
The average commit time is `r mean(experiment$tCommit)/1e6` milliseconds with 
a minimum of `r min(experiment$tCommit)/1e6` milliseconds and a maximum of `r max(experiment$tCommit)/1e6` milliseconds.
The distribution of the block execution time is shown below:

```{r, echo = FALSE}
experiment %>% 
  ggplot(aes(tBlock)) + 
  geom_freqpoly(binwidth = 10000)
```

The distribution of the commit time is shown below:

```{r, echo = FALSE}
experiment %>% 
  ggplot(aes(tCommit)) + 
  geom_freqpoly(binwidth = 10000)
```
