---
title: "Wallet Transfer Report on Mainnet"
date: "`r Sys.Date()`"
params:
  HwInfo: (Hardware Info)
  OsInfo: (OS Info)
  Machine: (Machine Info)
  GoInfo: (GO Info)
  GitHash: (GithubKey)
  StateDB: (StateDB)
  VM: (VM)
  db: ./profile.db
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
library(gt)

# open database
con <- dbConnect(SQLite(), params$db)

# load wallet transfers into a data frame
txData <- dbReadTable(con, 'txProfile') %>% filter(txType == 0)

# compress wallet transfer data for each 1M wallet transfers
tx_group_size <- 1000000
txData$tx_group <- 1:nrow(txData) %/% tx_group_size
reducedTxData <- txData %>% group_by(tx_group) %>% summarise(gas=mean(gas)/1e3) # average gas (in KGas)
reducedTxData$tx <- reducedTxData$tx_group * tx_group_size
reducedTxData$tx_group <- NULL

# close database connection
dbDisconnect(con)
```

The following report characterises wallet transfers on the mainnet.
Wallet transfers are found in the block range from **`r format(min(txData$block),big.mark=",")`**  to **`r format(max(txData$block),big.mark=",")`**.
The block range contains **`r format(count(txData), big.mark=",")`** wallet transfers.

The average gas consumption of wallet transfers is `r format(mean(txData$gas)/1e3, digits=3, nsmall=3)` KGas, with a minimum gas consumption of `r format(min(txData$gas)/1e3, digits=3, nsmall=3)` KGas and a maximum gas consumption of `r format(max(txData$gas)/1e6, digits=3, nsmall=3)` MGas.
The top seven most gas-consuming wallet transfers are the following:

```{r echo=FALSE, message=FALSE}
top7Transactions <- txData %>% top_n(7,gas) %>% arrange(desc(gas)) %>% select(block, tx, gas) %>% rename(Gas = gas, Block = block, Transaction = tx)
gt(top7Transactions)
```

The smoothened trend line of gas consumption over all wallet transfers is shown below.
In the figure, we aggregate the gas consumption for one million transactions shown as points.

```{r, echo=FALSE, message=FALSE}
reducedTxData %>%
  ggplot(aes(x = tx, y = gas)) +
  geom_smooth(color = "tomato") +
  geom_point(alpha=0.3) +
  labs(x="Transactions", y="KGas", title="Gas Consumption of Wallet Transfers")
```

The histogram with density function of wallet transfers' gas is shown below:

```{r, echo=FALSE, message=FALSE}
hist(txData$gas, main="Histogram for Wallet Transfers", freq=FALSE, xlab="Gas Consumption", col="lightblue1")
lines(density(txData$gas), col="dodgerblue3", lwd=2)
```

