---
title: "Request Processing Report"
date: "`r Sys.Date()`"
params:
  db: /var/opera/Aida/tmp-rapolt/register/test-f5-40w-xapi249-65.8m2.db
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
library(gt)

# open database
conn <- dbConnect(SQLite(), params$db)

# Fetch RunMetadata
Metadata <- dbSendQuery(conn, 'SELECT key, cast(value as text) as value FROM metadata;') %>% dbFetch

first <- Metadata %>% filter(key == "First")
last <- Metadata %>% filter(key == "Last")

# load block and transaction tables into data frames and exclude lachesis transition block
TxData <- dbReadTable(conn, 'stats_rpc') 

# close database connection
dbDisconnect(conn)
```

## ##############################################################################

## 1. Summary

```{r, echo=FALSE, message=FALSE}
maxReqRate <- TxData %>% filter(req_rate == max(req_rate)) %>% filter(count == min(count)) %>% distinct(req_rate, count) 
maxGasRate <- TxData %>% filter(gas_rate == max(gas_rate)) %>% filter(count == min(count)) %>% distinct(gas_rate, count) 
maxOverallReqRate <- TxData %>% filter(overall_req_rate == max(overall_req_rate)) %>% filter(count == min(count)) %>% distinct(overall_req_rate, count) 
maxOverallGasRate <- TxData %>% filter(overall_gas_rate == max(overall_gas_rate)) %>% filter(count == min(count)) %>% distinct(overall_gas_rate, count) 

runId <- Metadata %>% filter(key == "RunId")
runSucceed <- Metadata %>% filter(key == "RunSucceed")
runtime <- Metadata %>% filter(key == "Runtime")
runError <- Metadata %>% filter(key == "RunError")
isRunSuccess <- runSucceed$value == "true"

archiveMode <- Metadata %>% filter(key == "ArchiveMode")
isArchiveActive <- archiveMode$value == "true"

colorize <- function(x, color) {
	if (knitr::is_latex_output()) {
		sprintf("\\textcolor{%s}{%s}", color, x)
	} else if (knitr::is_html_output()) {
		sprintf("<span style='color: %s;'>%s</span>", color, x)
	} else x
}

fmt <- function(x, scale, unit, d) {
	paste(format(as.numeric(x) * scale, digit=d, nsmall=0), unit)
}

pluralize <- function(n, word) {
	if (n == 0) {
		""
	} else if (n == 1) {
		paste(n, word)
	} else {
		paste0(n, " ", word, "s")
	}
}

add_whitespace <- function(text) {
	if (text == "") {
		text
	} else {
		paste(text, " ")
	}
}

fmt_duration <- function(seconds) {
	paste0(
		add_whitespace(pluralize(floor(seconds / (24*60*60)), "day")),
		add_whitespace(pluralize(floor(seconds / (60*60)) %% 24 , "hour")),
		add_whitespace(pluralize(floor(seconds / 60) %% 60, "minute")),
		pluralize(seconds %% 60, "second")
	)
}

b <- function(text) {
	paste0("**", text, "**")
}

fmt_stateDb <- function(dbImpl, dbVariant, carmenSchema) {
	if (dbImpl == "geth") {
		dbImpl
	} else {
		paste0(b(dbImpl), "(", b(dbVariant), " ", b(carmenSchema), ")")
	}
}

```

Run `r runId$value` `r if(isRunSuccess){
	b(colorize(paste0("completed successfully"), "green"))
} else {
	b(colorize(paste0("failed"), "red"))
}`. The runtime is `r b(fmt_duration(as.numeric(runtime$value)))`.

    `r if(!isRunSuccess) {
        runError$value
    }`

```{r, echo=FALSE, message=FALSE}
rTx  <- data.frame(Property="Request Rate", Mean=fmt(mean(TxData$req_rate), 1, "ReqPS", 4), Max=fmt(max(TxData$req_rate), 1, "ReqPS", 4))
rGas <- data.frame(Property="Gas Rate", Mean=fmt(mean(TxData$gas_rate), 1e-6, "MGasPS", 4), Max=fmt(max(TxData$gas_rate), 1e-6, "MGasPS", 4))

summary <- rbind(rTx, rGas)

gt(summary)
```


## ##############################################################################

## 2. Experimental Setup

```{r, echo=FALSE, message=FALSE}
hostname <- Metadata %>% filter(key == "Hostname")
ip <- Metadata %>% filter(key == "IpAddress")
processor <- Metadata %>% filter(key == "Processor")
memory <- Metadata %>% filter(key == "Memory")
disks <- Metadata %>% filter(key == "Disks")
OsInfo <- Metadata %>% filter(key == "Os")
GoInfo <- Metadata %>% filter(key == "GoVersion")
aidaHash <- Metadata %>% filter(key == "AidaGitHash")
carmenHash <- Metadata %>% filter(key == "CarmenGitHash")
dbImpl <- Metadata %>% filter(key == "DbImpl")
dbVariant <- Metadata %>% filter(key == "DbVariant")
carmenSchema <- Metadata %>% filter(key == "CarmenSchema")
vmImpl <- Metadata %>% filter(key == "VmImpl")
dbSrc <- Metadata %>% filter(key == "DbSrc")
rpcRecordings <- Metadata %>% filter(key == "RpcRecordings")


```

The experiment is run on the machine **`r hostname$value`**(**`r ip$value`**), which is a **`r processor$value`**, **`r memory$value`** computer.
The operating system is **`r OsInfo$value`**.
The system has installed **`r GoInfo$value`**.

The github hash of the libraries are:

* Aida: `r b(aidaHash$value)`
* Carmen: `r b(carmenHash$value)`

For this experiment, the following configurations were made:

* StateDB: `r b(fmt_stateDb(dbImpl$value, dbVariant$value, carmenSchema$value))`
* Virtual Machine: `r b(vmImpl$value)`

StateDB used is stored under the path `r b(dbSrc$value)`. The RPC Recordings used is stored under the path `r b(rpcRecordings$value)`

The data set used for this experiment is stored in the database `r b(params$db)`.

## ##############################################################################

## 3. Request Rate

The average request rate is **`r format(mean(TxData$req_rate), big.mark=",", digit=4)`** ReqPS. The max transaction rate  is **`r format(maxReqRate$req_rate, big.mark=",", digit=4)`** ReqPS at request #**`r format(maxReqRate$count, big.mark=",")`**. 

The dashed line shows the average request rate achieve up until the request number.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8}
TxData %>% 
   mutate(req_rate = as.numeric(req_rate), count = as.numeric(count)) %>%
   ggplot(aes(x = count, y = req_rate)) +
   geom_line(aes(x = count, y = overall_req_rate), linetype = "longdash", color = "tomato") +
   geom_point(alpha=0.3) +
   scale_y_continuous(labels = scales::unit_format(unit="ReqPS")) +
   labs(x="Number of Requests", y="Request Rate (Requests Per Second)", title="Request Rate")
```

## ##############################################################################

## 4. Gas Rate

The average gas rate is **`r format(mean(TxData$gas_rate) * 1e-6, big.mark=",", digit=4)`** MGasPS. The max gas rate  is **`r format(maxGasRate$gas_rate * 1e-6, big.mark=",", digit=4)`** MGasPS at request #**`r format(maxGasRate$count, big.mark=",")`**. 

The dashed line shows the average gas rate achieve up until the request number.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8}
TxData %>% 
   mutate(gas_rate = as.numeric(gas_rate) * 1e-6, start = as.numeric(count), overall_gas_rate = as.numeric(overall_gas_rate) * 1e-6) %>%
   ggplot(aes(x = count, y = gas_rate)) +
   geom_line(aes(x = count, y = overall_gas_rate), linetype = "longdash", color = "tomato") +
   geom_point(alpha=0.3) +
   scale_y_continuous(labels = scales::unit_format(unit="MGasPS")) +
   labs(x="Number of Requests", y="Gas Rate (Million Gas Per Second)", title="Gas Rate")
```

