---
title: "F1 Report - Transaction Processing Time"
date: "`r Sys.Date()`"
params:
  HwInfo: (Hardware Info)
  OsInfo: (OS Info)
  Machine: (Machine Info)
  GoInfo: (GO Info)
  GitHash: (GithubKey)
  StateDB: (StateDB)
  VM: (VM)
  db: /var/opera/Aida/tmp-rapolt/register/s5-f1.db
  first: 479327
  last: 22832168
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
library(gt)

# open database
con <- dbConnect(SQLite(), params$db)

# load block and transaction tables into data frames and exclude lachesis transition block
TxData <- dbReadTable(con, 'stats') %>% filter(start >= params$first & end <= params$last)

# close database connection
dbDisconnect(con)
```

## 1. Experimental Setup
The experiment is run on the machine `r params$Machine`, which is a `r params$HwInfo` computer.
The operating system is `r params$OsInfo`.
The system has installed `r params$GoInfo`.
The github hash of the Aida repository is `r params$GitHash`.
For this experiment, we use **`r params$StateDB`** as a StateDB and **`r params$VM`** as a virtual machine.
The data set for this experiment is stored in the database `r params$db`.

## 2. Memory and Disk Usage

```{r, echo=FALSE, message=FALSE}
maxMemory <- TxData %>% filter(memory == max(memory))
maxDisk <- TxData %>% filter(disk == max(disk))
```

The experiment was conducted for the block range from **`r format(min(TxData$start),big.mark=",")`**  to **`r format(max(TxData$end),big.mark=",")`**.

Max RAM Usage throughout the run is **`r format(maxMemory$memory, big.mark=",")`** bytes at block height **`r format(maxMemory$start, big.mark=",")`**. 

```{r, echo=FALSE, message=FALSE}
TxData %>% mutate(memory = as.numeric(memory)) %>%
   ggplot(aes(x = start, y = memory)) +
   geom_point(alpha=0.3) +
   labs(x="Block Height", y="Ram Consumption (Bytes)", title="Memory Usage")
```

Max Disk Usage throughout the run is **`r format(maxMemory$disk, big.mark=",")`** bytes at block height **`r format(maxMemory$start, big.mark=",")`**

```{r, echo=FALSE, message=FALSE}
TxData %>% mutate(disk = as.numeric(disk)) %>%
   ggplot(aes(x = start, y = disk)) +
   geom_point(alpha=0.3) +
   labs(x="Block Height", y="Disk Consumption (Bytes)", title="Disk Usage")
```

## 3. Transaction Rate

```{r, echo=FALSE, message=FALSE}
maxTxRate <- TxData %>% filter(tx_rate == max(tx_rate))
```

On average, the transaction rate is **`r format(mean(TxData$tx_rate), big.mark=",")`** TPM. The max transaction rate  is **`r format(maxTxRate$tx_rate, big.mark=",")`** TPM at block height **`r format(maxTxRate$start, big.mark=",")`**. 

The dashed line shows the average transaction rate achieve up until the block height.

```{r, echo=FALSE, message=FALSE}
TxData %>% mutate(tx_rate = as.numeric(tx_rate)) %>%
   ggplot(aes(x = start, y = tx_rate)) +
   geom_line(aes(x = start, y = overall_tx_rate), linetype = "longdash", color = "tomato") +
   geom_point(alpha=0.3) +
   labs(x="Block Height", y="Transaction Per Minute", title="Transaction Rate")
```


## 4. Gas Rate

```{r, echo=FALSE, message=FALSE}
maxGasRate <- TxData %>% filter(gas_rate == max(gas_rate))
```
On average, the gas rate is **`r format(mean(TxData$gas_rate), big.mark=",")`** GPM. The max transaction rate  is **`r format(maxGasRate$gas_rate, big.mark=",")`** TPM at block height **`r format(maxGasRate$start, big.mark=",")`**. 

The dashed line shows the average gas rate achieve up until the block height.

```{r, echo=FALSE, message=FALSE}
TxData %>% mutate(gas_rate = as.numeric(gas_rate)) %>%
   ggplot(aes(x = start, y = gas_rate)) +
   geom_line(aes(x = start, y = overall_gas_rate), linetype = "longdash", color = "tomato") +
   geom_point(alpha=0.3) +
   labs(x="Block Height", y="Gas Per Minute", title="Gas Rate")
```

