---
title: "Block Processing Report"
date: "`r Sys.Date()`"
params:
  db: /var/opera/Aida/tmp-rapolt/register/s5-f1-test.db
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
library(gt)

# open database
con <- dbConnect(SQLite(), params$db)

# Fetch RunMetadata
Metadata <- dbSendQuery(con, 'SELECT key, cast(value as text) as value FROM metadata;') %>% dbFetch

first <- Metadata %>% filter(key == "First")
last <- Metadata %>% filter(key == "Last")

# load block and transaction tables into data frames and exclude lachesis transition block
TxData <- dbReadTable(con, 'stats') %>% 
	filter(start >= as.integer(first$value) & end <= as.integer(last$value)) %>%
	mutate(total_disk = as.numeric(live_disk) + as.numeric(archive_disk))


# close database connection
dbDisconnect(con)
```

## ##############################################################################

## 1. Summary

```{r, echo=FALSE, message=FALSE}
maxMemory <- TxData %>% filter(memory == max(memory)) %>% filter(start == min(start)) %>% distinct(memory, start) 
maxTotalDisk <- TxData %>% filter(total_disk == max(total_disk)) %>% filter(start == min(start)) %>% distinct(total_disk, start) 
maxLiveDisk <- TxData %>% filter(live_disk == max(live_disk)) %>% filter(start == min(start)) %>% distinct(live_disk, start) 
maxArchiveDisk <- TxData %>% filter(archive_disk == max(archive_disk)) %>% filter(start == min(start)) %>% distinct(archive_disk, start) 
maxTxRate <- TxData %>% filter(tx_rate == max(tx_rate)) %>% filter(start == min(start)) %>% distinct(tx_rate, start)
maxGasRate <- TxData %>% filter(gas_rate == max(gas_rate)) %>% filter(start == min(start)) %>% distinct(gas_rate, start) 

runId <- Metadata %>% filter(key == "RunId")
runSucceed <- Metadata %>% filter(key == "RunSucceed")
runtime <- Metadata %>% filter(key == "Runtime")
runError <- Metadata %>% filter(key == "RunError")
isRunSuccess <- runSucceed$value == "true"

archiveMode <- Metadata %>% filter(key == "ArchiveMode")
isArchiveActive <- archiveMode$value == "true"

colorize <- function(x, color) {
	if (knitr::is_latex_output()) {
		sprintf("\\textcolor{%s}{%s}", color, x)
	} else if (knitr::is_html_output()) {
		sprintf("<span style='color: %s;'>%s</span>", color, x)
	} else x
}

fmt <- function(x, scale, unit, d) {
	paste(format(as.numeric(x) * scale, digit=d, nsmall=0), unit)
}

pluralize <- function(n, word) {
	if (n == 0) {
		""
	} else if (n == 1) {
		paste(n, word)
	} else {
		paste0(n, " ", word, "s")
	}
}

add_whitespace <- function(text) {
	if (text == "") {
		text
	} else {
		paste(text, " ")
	}
}

fmt_duration <- function(seconds) {
	paste0(
		add_whitespace(pluralize(floor(seconds / (24*60*60)), "day")),
		add_whitespace(pluralize(floor(seconds / (60*60)) %% 24 , "hour")),
		add_whitespace(pluralize(floor(seconds / 60) %% 60, "minute")),
		pluralize(seconds %% 60, "second")
	)
}

b <- function(text) {
	paste0("**", text, "**")
}

```

Run `r runId$value` `r if(isRunSuccess){
	b(colorize(paste0("completed successfully"), "green"))
} else {
	b(colorize(paste0("failed"), "red"))
}`. The runtime is `r b(fmt_duration(as.numeric(runtime$value)))`.

    `r if(!isRunSuccess) {
        runError$value
    }`

```{r, echo=FALSE, message=FALSE}
rTx  <- data.frame(Property="Transaction Rate", Mean=fmt(mean(TxData$tx_rate), 1, "TPS", 4), Max=fmt(max(TxData$tx_rate), 1, "TPS", 4))
rGas <- data.frame(Property="Gas Rate", Mean=fmt(mean(TxData$gas_rate), 1e-6, "MGasPS", 4), Max=fmt(max(TxData$gas_rate), 1e-6, "MGasPS", 4))
rMem <- data.frame(Property="Memory", Mean="", Max=fmt(max(TxData$memory), 1e-9, "GB", 4))
rLDb <- data.frame(Property="Disk - LiveDB", Mean="", Max=fmt(max(TxData$live_disk), 1e-9, "GB", 4))
rADb <- data.frame(Property="Disk - ArchiveDB", Mean="", Max=fmt(max(TxData$archive_disk), 1e-9, "GB", 4))
rTDb <- data.frame(Property="Disk - Total", Mean="", Max=fmt(max(TxData$total_disk), 1e-9, "GB", 4))

summary <- rbind(rTx, rGas, rMem, rLDb)

if (isArchiveActive) {
	summary <- rbind(summary, rADb)
	summary <- rbind(summary, rTDb)
}

gt(summary)
```


## ##############################################################################

## 2. Experimental Setup

```{r, echo=FALSE, message=FALSE}
hostname <- Metadata %>% filter(key == "Hostname")
ip <- Metadata %>% filter(key == "IpAddress")
processor <- Metadata %>% filter(key == "Processor")
memory <- Metadata %>% filter(key == "Memory")
disks <- Metadata %>% filter(key == "Disks")
OsInfo <- Metadata %>% filter(key == "Os")
GoInfo <- Metadata %>% filter(key == "GoVersion")
aidaHash <- Metadata %>% filter(key == "AidaGitHash")
carmenHash <- Metadata %>% filter(key == "CarmenGitHash")
dbImpl <- Metadata %>% filter(key == "DbImpl")
dbVariant <- Metadata %>% filter(key == "DbVariant")
carmenSchema <- Metadata %>% filter(key == "CarmenSchema")
vmImpl <- Metadata %>% filter(key == "VmImpl")
```

The experiment is run on the machine **`r hostname$value`**(**`r ip$value`**), which is a **`r processor$value`**, **`r memory$value`** computer.
The operating system is **`r OsInfo$value`**.
The system has installed **`r GoInfo$value`**.

The github hash of the libraries are:

* Aida: **`r aidaHash$value`**
* Carmen: **`r carmenHash$value`**

For this experiment, we use **`r dbImpl$value`**(**`r dbVariant$value`** **`r carmenSchema$value`**) as a StateDB and **`r vmImpl$value`** as a virtual machine.  The data set for this experiment is stored in the database **`r params$db`**.

## ##############################################################################

## 3. Transaction Rate

The average transaction rate is **`r format(mean(TxData$tx_rate), big.mark=",", digit=4)`** TPS. The max transaction rate  is **`r format(maxTxRate$tx_rate, big.mark=",", digit=4)`** TPS at block height **`r format(maxTxRate$start, big.mark=",")`**. 

The dashed line shows the average transaction rate achieve up until the block height.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8}
TxData %>% 
   mutate(tx_rate = as.numeric(tx_rate), start = as.numeric(start) * 1e-6) %>%
   ggplot(aes(x = start, y = tx_rate)) +
   geom_line(aes(x = start, y = overall_tx_rate), linetype = "longdash", color = "tomato") +
   geom_point(alpha=0.3) +
   scale_x_continuous(labels = scales::unit_format(unit="M")) +
   labs(x="Block Height", y="Transaction Per Second", title="Transaction Rate")
```

## ##############################################################################

## 4. Gas Rate

The average gas rate is **`r format(mean(TxData$gas_rate) * 1e-6, big.mark=",", digit=4)`** MGasPS. The max gas rate  is **`r format(maxGasRate$gas_rate * 1e-6, big.mark=",", digit=4)`** MGasPS at block height **`r format(maxGasRate$start, big.mark=",")`**. 

The dashed line shows the average gas rate achieve up until the block height.

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8}
TxData %>% 
   mutate(gas_rate = as.numeric(gas_rate) * 1e-6, start = as.numeric(start) * 1e-6, overall_gas_rate = as.numeric(overall_gas_rate) * 1e-6) %>%
   ggplot(aes(x = start, y = gas_rate)) +
   geom_line(aes(x = start, y = overall_gas_rate), linetype = "longdash", color = "tomato") +
   geom_point(alpha=0.3) +
   scale_x_continuous(labels = scales::unit_format(unit="M")) +
   scale_y_continuous(labels = scales::unit_format(unit="MGasPS")) +
   labs(x="Block Height", y="Million Gas Per Second", title="Gas Rate")
```

## ##############################################################################

## 5. Memory and Disk Usage


The experiment was conducted for the block range from **`r format(min(TxData$start),big.mark=",")`**  to **`r format(max(TxData$end),big.mark=",")`**.

Max RAM Usage throughout the run is **`r format(as.numeric(maxMemory$memory) * 1e-9, big.mark=",", digit=3)`** GB at block height **`r format(maxMemory$start, big.mark=",")`**. 

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8}
TxData %>% mutate(memory = as.numeric(memory) * 1e-9, start = as.numeric(start) * 1e-6) %>%
   ggplot(aes(x = start, y = memory)) +
   geom_point(alpha=0.3) +
   scale_x_continuous(labels = scales::unit_format(unit="M")) +
   scale_y_continuous(labels = scales::unit_format(unit="GB")) +
   labs(x="Block Height", y="Ram Consumption", title="Memory Usage")
```


`r if(isArchiveActive){
paste(
	paste0("Total Disk Usage throughout the run is ", b(format(as.numeric(maxTotalDisk$total_disk) * 1e-9, big.mark=",", digit=3)), " GB at block height ", b(format(maxTotalDisk$start, big.mark=",")), " - " ),
	paste0("Live: ",  b(fmt(as.numeric(maxLiveDisk$live_disk), 1e-9, "GB", 4)), "(", fmt(100 * as.numeric(maxLiveDisk$live_disk) / as.numeric(maxTotalDisk$total_disk), 1, "%", 3), "), "),
	paste0("Archive: ",  b(fmt(as.numeric(maxArchiveDisk$archive_disk), 1e-9, "GB", 4)), "(", fmt(100 * as.numeric(maxArchiveDisk$archive_disk) / as.numeric(maxTotalDisk$total_disk), 1, "%", 3), ").")
)

} else {

paste0("Max Live Disk Usage throughout the run is ", b(format(as.numeric(maxLiveDisk$live_disk) * 1e-9, big.mark=",", digit=3)), " GB at block height ", b(format(maxLiveDisk$start, big.mark=",")), ".")

}`

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8, eval=!isArchiveActive}
TxData %>% mutate(live_disk = as.numeric(live_disk) * 1e-9, start = as.numeric(start) * 1e-6) %>%
   ggplot(aes(x = start, y = live_disk)) +
   geom_point(alpha=0.3) +
   scale_x_continuous(labels = scales::unit_format(unit="M")) +
   scale_y_continuous(labels = scales::unit_format(unit="GB")) +
   labs(x="Block Height", y="Disk Consumption", title="Disk Usage")
```

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=8, eval=isArchiveActive}
ArchivedTxData <- TxData %>%
   mutate(live_disk = as.numeric(live_disk) * 1e-9, archive_disk = as.numeric(archive_disk) * 1e-9, total_disk = as.numeric(total_disk) * 1e-9, start = as.numeric(start) * 1e-6)

ggplot() +
   geom_point(data = ArchivedTxData, aes(x = start, y = total_disk, color="Total"), color="black", alpha=0.3) +
   geom_point(data = ArchivedTxData, aes(x = start, y = live_disk, color="Live"), alpha=0.3) +
   geom_point(data = ArchivedTxData, aes(x = start, y = archive_disk, color="Archive"), alpha=0.3) +
   scale_x_continuous(labels = scales::unit_format(unit="M")) +
   scale_y_continuous(labels = scales::unit_format(unit="GB")) +
   labs(x="Block Height", y="Disk Consumption", title="Disk Usage", color="Legend") +
   theme(legend.justification = c(0, 1), legend.position = c(0.025, 0.975))
```


