---
title: "Contract Creation Report on Mainnet"
date: "`r Sys.Date()`"
params:
  HwInfo: (Hardware Info)
  OsInfo: (OS Info)
  Machine: (Machine Info)
  GoInfo: (GO Info)
  GitHash: (GithubKey)
  StateDB: (StateDB)
  VM: (VM)
  db: ./profile.db
---

```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(RSQLite)
library(gt)

# open database
con <- dbConnect(SQLite(), params$db)

# load contract creations into a data frame
txData <- dbReadTable(con, 'txProfile') %>% filter(txType == 1)

# compress contract creation data for each 1M contract creations
tx_group_size <- 1000000
txData$tx_group <- 1:nrow(txData) %/% tx_group_size
reducedTxData <- txData %>% group_by(tx_group) %>% summarise(gas=mean(gas)/1e3) # average gas (in KGas)
reducedTxData$tx <- reducedTxData$tx_group * tx_group_size
reducedTxData$tx_group <- NULL

# close database connection
dbDisconnect(con)
```

The following report characterises contract creations on the mainnet.
Contract creations are found in the block range from **`r format(min(txData$block),big.mark=",")`**  to **`r format(max(txData$block),big.mark=",")`**.
The block range contains **`r format(count(txData), big.mark=",")`** contract creations.

The average gas consumption of contract creations is `r format(mean(txData$gas)/1e3, digits=3, nsmall=3)` KGas, with a minimum gas consumption of `r format(min(txData$gas)/1e3, digits=3, nsmall=3)` KGas and a maximum gas consumption of `r format(max(txData$gas)/1e6, digits=3, nsmall=3)` MGas.
The top seven most gas-consuming contract creations are the following:

```{r echo=FALSE, message=FALSE}
top7Transactions <- txData %>% top_n(7,gas) %>% arrange(desc(gas)) %>% select(block, tx, gas) %>% rename(Gas = gas, Block = block, Transaction = tx)
gt(top7Transactions)
```

The histogram with density function of contract creations' gas is shown below:

```{r, echo=FALSE, message=FALSE}
hist(txData$gas, main="Histogram for Contract Creations", freq=FALSE, xlab="Gas Consumption", col="lightblue1")
lines(density(txData$gas), col="dodgerblue3", lwd=2)
```
